Visible Minorities and Economic Inequality: An Examination of Rosedale-Moore Park and Downtown Yonge East

### 2024-09-27 outputs/paper/paper.qmd
fixing issue of one missing value in education figure

## Graphing education data
# Define the ordered education categories
education_categories <- c("No certificate, diploma or degree",
                          "High school diploma or equivalency certificate", 
                          "Postsecondary certificate or diploma",
                          "Apprenticeship or trades certificate or diploma",
                          "Non-apprenticeship trades certificate or diploma",
                          "College, CEGEP or other non-university certificate or diploma",
                          "University certificate or diploma below bachelor level",
                          "Bachelor's degree",
                          "University certificate or diploma above bachelor level",
                          "Degree in medicine, dentistry, veterinary medicine or optometry",
                          "Master's degree", "Earned doctorate")

>>>>

## Graphing education data
# Define the ordered education categories
education_categories <- c("No certificate, diploma or degree",
                          "High (secondary) school diploma or equivalency certificate", 
                          "Postsecondary certificate or diploma",
                          "Apprenticeship or trades certificate or diploma",
                          "Non-apprenticeship trades certificate or diploma",
                          "College, CEGEP or other non-university certificate or diploma",
                          "University certificate or diploma below bachelor level",
                          "Bachelor's degree",
                          "University certificate or diploma above bachelor level",
                          "Degree in medicine, dentistry, veterinary medicine or optometry",
                          "Master's degree", "Earned doctorate")
